% ---
% Dylan Gardner's Resume
% ---

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[12pt,letterpaper,final]{moderncv}
\usepackage{fontspec}
\moderncvtheme[blue]{classic}

% Document Layout
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
\usepackage[utf8]{inputenc}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode


% Personal Information
\firstname{Dylan}
\familyname{Gardner}
\extrainfo{Salt Lake City, Utah}
\email{dylan@gardnermedia.com}
\mobile{Redacted Phone. Email for unredacted copy.}
\homepage{dylngg.github.io}

\title{Dylan Gardner's Resume}

\nopagenumbers{}

\begin{document}

% Document Modifications
\closesection{}
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

\maketitle

\section{Programming Languages \& Skills}
  \cvline{}{Python, Golang, Linux sysadmin, C, C++, Git, Bash, PostgreSQL, HTML/CSS, Javascript} \\
\section{Education}
  \cventry{Fall 2020}{B.S. Computer Science}{University of Utah}{}{GPA: 3.475}{}
  \cvlistitem{Data Structures and Algorithms}
  \cvlistitem{Operating Systems}
  \cvlistitem{Distributed Systems} \\
\section{Experience}
  \cventry{March 2018 -- Present}{Technical Assistant}{Center For High Performance Computing (CHPC)}{University of Utah}{}{
      \begin{itemize}
          \item Researched and collaborated on a Linux daemon in Python called Arbiter2 that automated enforcement of acceptable usage policies on shared nodes; \emph{Used at CHPC and a number of other HPC centers nationwide}.
          \item Published a ACM \textcolor{addresscolor}{\link[paper]{https://dylngg.github.io/resources/arbiterTechPaper.pdf}} on the software above that was presented at a national HPC conference (PEARC). Won best \textcolor{addresscolor}{\link[poster]{https://dylngg.github.io/resources/arbiterRMACC19Poster.pdf}} award for that software at a regional HPC conference (RMACC).
        \item Collaborating on a project to improve monitoring of CHPC's environment and network traffic using Prometheus, InfluxDB, SNMP and Grafana. \\
      \end{itemize}
  }
  \cventry{Summer 2020}{High Performance Computing Intern}{Idaho National Laboratory}{Idaho Falls, ID}{}{
    \begin{itemize}
        \item Worked with a fellow intern to bring a 15x speedup on a Python-based sensitive text obfuscator by creating a trie-based plaintext and regex optimizer.
        \item Developed a user monitoring system using PostgreSQL to monitor logins/logouts across nodes. \\
      % \item Measured and analyzed the performance impacts of node monitoring daemons on various High Performance Computing workloads. \\
    \end{itemize}
  }
  \cventry{Summer 2016}{Networking Intern}{Canyons School District}{Sandy, UT}{}{
    \begin{itemize}
      \item Set up, planned and configured network switches and access points with local school administrators from across the district.
      \item Helped create a Java application that led to \~{}2x faster configuration of switches. \\
    \end{itemize}
  }
\section{Projects}
  \cventry{}{Salt Lake City Crime Heatmap}{}{A interactive Javascript heatmap of Salt Lake City crime parsed and converted using Python \& Pandas from open source data.}{At \textcolor{addresscolor}{\link[dylngg.github.io/slc-crime-heatmap/]{https://dylngg.github.io/slc-crime-heatmap/}}}{}
  \cventry{}{Discord Email Notifier}{}{Developed a Python daemon using Discord's API to batch notifications to a email.}{At \textcolor{addresscolor}{\link[github.com/dylngg/discord-notification-emailer]{https://github.com/dylngg/discord-notification-emailer}}}{}
  \cventry{}{userctl}{}{Currently developing a Linux D-Bus daemon in C that sets configurable limits on users and groups with systemd cgroups.}{At \textcolor{addresscolor}{\link[github.com/dylngg/userctl]{https://github.com/dylngg/userctl}}}{}
\end{document}

